---
title: "Presentation Shiny app"
author: "Rosina Plomp"
date: "May 20, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App idea
This app will show two common type of functions -- linear and exponential. 

## ui.R code - pt1
The ui.R code specifies the layout -- a sidebar containing two checkboxes and a main panel divided in two containing two plots.
```{r ui1, message=FALSE, warning=FALSE, eval=FALSE,echo=T}
# Define UI 
shinyUI(fluidPage(
  # Application title
  titlePanel("Types of functions"),
  # Sidebar 
  sidebarLayout(
    sidebarPanel(
       checkboxInput("linear", "linear", value=FALSE), 
        checkboxInput("exponential", "exponential", value=FALSE)),
```
## ui.R code - pt2
The ui.R code specifies the layout -- a sidebar containing two checkboxes and a main panel divided in two containing two plots.
```{r ui2, message=FALSE, warning=FALSE, eval=FALSE,echo=T}
    # Show a plot of the generated distribution
    mainPanel(
              fluidRow(
                splitLayout(style = "border: 1px solid silver:", 
                            cellWidths = c(300,300), 
                            plotOutput("plotgraph1"), 
                            plotOutput("plotgraph2")
                ))))))
```
## server.R code - pt1
In the server.R code, two sets of x and y coordinates are generated and plotted. 
```{r server1, message=FALSE, warning=FALSE, eval=FALSE,echo=T}
#define data
  x_lin<-c(1:100)
  y_lin<-x_lin
  x_exp<-c(1:100)
  y_exp<-(x_exp)^2
```
## server.R code - pt2
```{r server2, message=FALSE, warning=FALSE, eval=FALSE,echo=T}
# Define server logic required to draw plots
shinyServer(function(input, output) {
    plotlin <- reactive({
      input$linear
      if (input$linear){
        return(plot(y_lin~x_lin, 
            main="Linear function (y~x)",xlab="x",ylab="y",col="blue"))
      } else {return(NULL)}})
    plotexp <- reactive({
      input$exponential
      if (input$exponential){
        return(plot(y_exp~x_exp,
            main="Exponential function (y~x^2)",xlab="x",ylab="y",col="green"))
      } else {return(NULL)}})   
    output$plotgraph1 = renderPlot({plotlin()})
    output$plotgraph2 = renderPlot({plotexp()})})
```


